### 2018-04-10 latex/icpp18/experiments.tex
synthetic dataset

{\em Synthetic:} For synthetic sparse matrices, we used the popular Kronecker generator from Graph500 benchmark (\url{http://www.graph500.org/}). The graph generator is a Kronecker generator similar to the Recursive MATrix (R-MAT) scale-free graph generation algorithm \cite{CZF04}. This model recursively sub-divides the adjacency matrix of the graph into four equal-sized partitions and distributes edges within these partitions with unequal probabilities. Initially, the adjacency matrix is empty, and edges are added one at a time. The parameters to the generator are the number of vertices $N$ and the Edge Factor ($ef$) that defines the ratio of the graph?s edge count to its vertex count (i.e., half the average degree of a vertex in the graph). Typically, the number of edges $M$ of the scale free graph will be $ef \times N$. In our case, we consider $2^{20}$($\approx$ 1.05 million) vertices and set of edge factor $ef$=\{4,8,16,32,64\}.

>>>>

{\em Synthetic:} For synthetic sparse matrices, we used the popular Kronecker generator from Graph500 benchmark (\url{http://www.graph500.org/}). The graph generator is a Kronecker generator similar to the Recursive MATrix (R-MAT) scale-free graph generation algorithm \cite{CZF04}. This model recursively sub-divides the adjacency matrix of the graph into four equal-sized partitions and distributes edges within these partitions with unequal probabilities. Initially, the adjacency matrix is empty, and edges are added one at a time. The parameters to the generator are the number of vertices $N$ and the Edge Factor ($ef$) that defines the ratio of the graph's edge count to its vertex count (i.e., half the average degree of a vertex in the graph). Typically, the number of edges $M$ of the scale free graph will be $ef \times N$. In our case, we consider $2^{20}$($\approx$ 1.05 million) vertices and set of edge factor $ef$=\{4,8,16,32,64\}.
